Example of Market Simulator Dasbhaord

### 2020-12-18 dashboard_example.Rmd
reformating for product and segments instead of org and persona

# Default configurations
prod_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'org_data_default.csv')
  )
per_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'per_data_default.csv')
  )
```

```{r prod-reactive-table}
# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

# prod configuration reactive element
prod_reactive <- reactive({
  # prod 1
  org_table$org1_value <- 0
  org_table$org1_value[org_table$levels %in% input$org1_org] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_issue] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_fin_trans] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_fin_account] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_funding] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_host_gov] <- 1

  # prod 2
  org_table$org2_value <- 0
  org_table$org2_value[org_table$levels %in% input$org2_org] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_issue] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_fin_trans] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_fin_account] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_funding] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_host_gov] <- 1

  # prod 3
  org_table$org3_value <- 0
  org_table$org3_value[org_table$levels %in% input$org3_org] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_issue] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_fin_trans] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_fin_account] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_funding] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_host_gov] <- 1

  # prod 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})
```

```{r persona-reactive-table}
# Assign covariate labels
per_table <- data.frame(
  levels = c(
    # Intercept
    "Intercept",
    # Mediums to follow news
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app",
    # Gender
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender",
    # Marital status
    "Widowed",
    "Divorced",
    "Separated",
    "Never married",
    # Education
    "High school graduate", 
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate",
    # Income
    "More than median of $61,372", 
    # Race
    "White", 
    "Black or African American", 
    "American Indian or Alaskan Native", 
    "Asian", 
    "Native Hawaiian or Pacific Islander",
    "Other race",
    # Age
    "More than median age of 36"
  )
)

## Test to subset the data
per_join <- per_default %>% inner_join(per_table, by = "levels")

# Persona configuration reactive element
per_reactive <- reactive({
  # Persona 1
  per_table$per1_value <- 0
  per_table$per1_value[per_table$levels == 'Intercept'] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_news_medium] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_gender] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_marital_status] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_education] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_income] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_race] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_age] <- 1

  # Persona 2
  per_table$per2_value <- 0
  per_table$per2_value[per_table$levels == 'Intercept'] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_gender] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_marital_status] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_education] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_income] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_race] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_age] <- 1

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})
```

@@

```{r compute-and-plot}
# Compute and render the market share plot
renderPlotly({
  org_choice = org_reactive()
  per_choice = per_reactive()

  # Persona 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])

  # Persona 1 expected utilities
  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))

  # Persona 1 market shares
  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)

  # Persona 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))

  # Persona 2 market shares
  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)

  # Persona 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Persona 3 expected utilities
  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))

  # Persona 3 market shares
  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)

  # Data for plotly
  plot_data <- data.frame(
    Value = c(
      # Persona 1
      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
      # Persona 2
      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
      # Persona 3
      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
    ),
    Product = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  )

  ggplotly(
    plot_data %>% 
      # Factor Product and Persona with ordered=TRUE
      mutate(
        Product = factor(
          Product, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Product, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})

# Compute and render the market share as a table
renderTable({
  org_choice = org_reactive()
  per_choice = per_reactive()

  # Persona 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])

  # Persona 1 expected utilities
  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))

  # Persona 1 market shares
  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)

  # Persona 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))

  # Persona 2 market shares
  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)

  # Persona 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Persona 3 expected utilities
  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))

  # Persona 3 market shares
  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)

  # Table
  data <- data.frame(
    Shares = c(
      # Persona 1
      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
      # Persona 2
      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
      # Persona 3
      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
    ),
    Product = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  ) %>% 
    pivot_wider(names_from = Persona, values_from = Shares)

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Product Name:",
  value = "Product 1",
  placeholder = "Enter Product Name",
  width = "450px"
)

# Product
renderUI({
  org_data = product_data()
  selectInput(
    "org1_org",
    label = "Product:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  org_data = product_data()
  selectInput(
    "org1_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Emergency response",
    selected = ifelse(
      sum(org_data[5:7,2]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  org_data = product_data()
  selectInput(
    "org1_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  org_data = product_data()
  selectInput(
    "org1_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  org_data = product_data()
  selectInput(
    "org1_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,2]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  org_data = product_data()
  selectInput(
    "org1_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

```{r org2-inputs}
# Naming
textInput(
  "org2_name",
  label = "Product Name:",
  value = "Product 2",
  placeholder = "Enter Product Name",
  width = "450px"
)

>>>>

# Default configurations
prod_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'org_data_default.csv')
  )
seg_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'per_data_default.csv')
  )
```

```{r prod-reactive-table}
# Assign level labels
prod_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

# prod configuration reactive element
prod_reactive <- reactive({
  # prod 1
  prod_table$prod1_value <- 0
  prod_table$prod1_value[prod_table$levels %in% input$prod1_prod] <- 1
  prod_table$prod1_value[prod_table$levels %in% input$prod1_issue] <- 1
  prod_table$prod1_value[prod_table$levels %in% input$prod1_fin_trans] <- 1
  prod_table$prod1_value[prod_table$levels %in% input$prod1_fin_account] <- 1
  prod_table$prod1_value[prod_table$levels %in% input$prod1_funding] <- 1
  prod_table$prod1_value[prod_table$levels %in% input$prod1_host_gov] <- 1

  # prod 2
  prod_table$prod2_value <- 0
  prod_table$prod2_value[prod_table$levels %in% input$prod2_prod] <- 1
  prod_table$prod2_value[prod_table$levels %in% input$prod2_issue] <- 1
  prod_table$prod2_value[prod_table$levels %in% input$prod2_fin_trans] <- 1
  prod_table$prod2_value[prod_table$levels %in% input$prod2_fin_account] <- 1
  prod_table$prod2_value[prod_table$levels %in% input$prod2_funding] <- 1
  prod_table$prod2_value[prod_table$levels %in% input$prod2_host_gov] <- 1

  # prod 3
  prod_table$prod3_value <- 0
  prod_table$prod3_value[prod_table$levels %in% input$prod3_prod] <- 1
  prod_table$prod3_value[prod_table$levels %in% input$prod3_issue] <- 1
  prod_table$prod3_value[prod_table$levels %in% input$prod3_fin_trans] <- 1
  prod_table$prod3_value[prod_table$levels %in% input$prod3_fin_account] <- 1
  prod_table$prod3_value[prod_table$levels %in% input$prod3_funding] <- 1
  prod_table$prod3_value[prod_table$levels %in% input$prod3_host_gov] <- 1

  # prod 4
  prod_table$prod4_value <- 0
  prod_table$prod4_value[prod_table$levels %in% input$prod4_prod] <- 1
  prod_table$prod4_value[prod_table$levels %in% input$prod4_issue] <- 1
  prod_table$prod4_value[prod_table$levels %in% input$prod4_fin_trans] <- 1
  prod_table$prod4_value[prod_table$levels %in% input$prod4_fin_account] <- 1
  prod_table$prod4_value[prod_table$levels %in% input$prod4_funding] <- 1
  prod_table$prod4_value[prod_table$levels %in% input$prod4_host_gov] <- 1
  prod_table
})
```

```{r persona-reactive-table}
# Assign covariate labels
seg_table <- data.frame(
  levels = c(
    # Intercept
    "Intercept",
    # Mediums to follow news
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app",
    # Gender
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender",
    # Marital status
    "Widowed",
    "Divorced",
    "Separated",
    "Never married",
    # Education
    "High school graduate", 
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate",
    # Income
    "More than median of $61,372", 
    # Race
    "White", 
    "Black or African American", 
    "American Indian or Alaskan Native", 
    "Asian", 
    "Native Hawaiian or Pacific Islander",
    "Other race",
    # Age
    "More than median age of 36"
  )
)

## Test to subset the data
seg_join <- seg_default %>% inner_join(seg_table, by = "levels")

# Persona configuration reactive element
seg_reactive <- reactive({
  # Persona 1
  seg_table$per1_value <- 0
  seg_table$per1_value[seg_table$levels == 'Intercept'] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_news_medium] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_gender] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_marital_status] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_education] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_income] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_race] <- 1
  seg_table$per1_value[seg_table$levels %in% input$per1_age] <- 1

  # Persona 2
  seg_table$per2_value <- 0
  seg_table$per2_value[seg_table$levels == 'Intercept'] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_gender] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_marital_status] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_education] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_income] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_race] <- 1
  seg_table$per2_value[seg_table$levels %in% input$per2_age] <- 1

  # Persona 3
  seg_table$per3_value <- 0
  seg_table$per3_value[seg_table$levels == 'Intercept'] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_news_medium] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_gender] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_marital_status] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_education] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_income] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_race] <- 1
  seg_table$per3_value[seg_table$levels %in% input$per3_age] <- 1
  seg_table
})
```

@@

```{r compute-and-plot}
# Compute and render the market share plot
renderPlotly({
  prod_choice = prod_reactive()
  seg_choice = seg_reactive()

  # Segment 1 predicted betas
  seg1_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,2])

  # Segment 1 expected utilities
  seg1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg1_betas))
  seg1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg1_betas))
  seg1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg1_betas))
  seg1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg1_betas))

  # Segment 1 market shares
  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)

  # Segment 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Segment 2 expected utilities
  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))

  # Segment 2 market shares
  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)

  # Segment 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Segment 3 expected utilities
  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))

  # Segment 3 market shares
  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)

  # Data for plotly
  plot_data <- data.frame(
    Value = c(
      # Segment 1
      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
      # Segment 2
      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
      # Segment 3
      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  )

  ggplotly(
    plot_data %>% 
      # Factor Product and Segment with ordered=TRUE
      mutate(
        Product = factor(
          Product, 
          levels = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Product, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})

# Compute and render the market share as a table
renderTable({
  prod_choice = prod_reactive()
  per_choice = per_reactive()

  # Segment 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])

  # Segment 1 expected utilities
  per1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per1_betas))
  per1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per1_betas))
  per1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per1_betas))
  per1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per1_betas))

  # Segment 1 market shares
  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)

  # Segment 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Segment 2 expected utilities
  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))

  #  Segment 2 market shares
  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)

  # Segment 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Segment 3 expected utilities
  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))

  # Segment 3 market shares
  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)

  # Table
  data <- data.frame(
    Shares = c(
      # Segment 1
      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
      # Segment 2
      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
      # Segment 3
      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  ) %>% 
    pivot_wider(names_from = Persona, values_from = Shares)

@@

```{r prod1-inputs}
# Naming
textInput(
  "prod1_name",
  label = "Product Name:",
  value = "Product 1",
  placeholder = "Enter Product Name",
  width = "450px"
)

# Product
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_prod",
    label = "Product:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(prod_data[1:4,][which(prod_data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Emergency response",
    selected = ifelse(
      sum(prod_data[5:7,2]) == 0, "Emergency response",
      as.character(prod_data[5:7,][which(prod_data[5:7,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(prod_data[8,2]) == 0, "Doesn’t engage in financial transparency",
      as.character(prod_data[8,][which(prod_data[8,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(prod_data[9,2]) == 0, "Doesn’t engage in financial accountability",
      as.character(prod_data[9,][which(prod_data[9,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(prod_data[10:11,2]) == 0, "Many small private donations",
      as.character(prod_data[10:11,][which(prod_data[10:11,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  prod_data = product_data()
  selectInput(
    "prod1_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(prod_data[12:13,2]) == 0, "Friendly relationship with government",
      as.character(prod_data[12:13,][which(prod_data[12:13,2] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

```{r prod2-inputs}
# Naming
textInput(
  "prod2_name",
  label = "Product Name:",
  value = "Product 2",
  placeholder = "Enter Product Name",
  width = "450px"
)
